Symbolic Weighted Language Models and\\ Quantitative Parsing over Infinite Alphabets

### 2021-10-05 main.tex
revision presentation algo best-search

%\noindent\quad
%\textbf{for all} $q_0, q_3 \in Q$
\Update $d_\bot$ if $\< q_1, q_2>$ was extracted (see Figure~\ref{fig:best-update-bottom}), or $d_\top$ 
if it was $\< q_1, p, q_2>$
(see Figure~\ref{fig:best-update-top}).$\;$
}
\caption{Best search for \SWVPA}
\label{algo:Dijkstra}
\end{algorithm}

@@

\begin{figure}[ht]
For every $q_0, q_3 \in Q$ and $p' \in P$, if $\< q_1, q_2> \notin \Q$ 
\[
\begin{array}{lcl}
%\multicolumn{3}{l}{\mathrm{For~all~} q_0, q_3 \in Q, p \in P,}\\
%
d_\bot(q_1, q_3) & \opluseq &
  d_\bot(q_1, q_2) \otimes
  \displaystyle\bigoplus_{\Deltai} \weiei(q_2, q_3)\\
%
d_\bot(q_0, q_3) & \opluseq &
  {\displaystyle\bigoplus_{\Deltac}}
  \bigl(
  \weiec(q_0, p', q_1) \otimes
   d_\top(q_1, p', q_2) \otimes
  \displaystyle\bigoplus_{\Deltar} \weir(q_2, p', q_3)\bigr)\\
%
d_\bot(q_1, q_3) & \opluseq &
  d_\bot(q_1, q_2) \otimes
  \displaystyle\bigoplus_{\Deltar} \weier(q_2, q_3)\\
%
d_\bot(q_1, q_3) & \opluseq &
  d_\bot(q_1, q_2) \otimes d_\bot(q_2, q_3)\  \mathrm{if~} \< q_2, q_3> \notin \Q \\
\end{array}
\]
\caption{The update $d_\top$ when $\< q_1, q_2> \notin \Q$.}
\label{fig:best-update-bottom}
\end{figure}
%

\begin{figure}[ht]
For every $q_0, q_3 \in Q$ and $p' \in P$, if $\< q_1, p, q_2> \notin \Q$
\[
\begin{array}{lcl}
d_\top(q_1, p, q_3) & \opluseq &
  d_\top(q_1, p, q_2) \otimes
  \displaystyle\bigoplus_{\Deltai} \weii(q_2, p, q_3)\\
%\multicolumn{3}{l}{\quad
%\mathrm{where~} \weii(q_2, p, q_3)_a \in \Phic
%\mathrm{~is~the~partial~application~}
%x_c \mapsto \weii(q_2, x_c, p, a, q_3)}\\
d_\top(q_0, p', q_3) & \opluseq &
  {\displaystyle\bigoplus_{\Deltac}}^2
  \bigl[ \bigl( \weic(q_0, p', q_1, p) \otimes_2
  d_\top(q_1, p, q_2) \bigr) \otimes_2
  {\displaystyle\bigoplus_{\Deltar}} \weir(q_2, p, q_3) \bigr]\\
%\multicolumn{3}{l}{\quad
%\mathrm{where~} \weic(q_0, p, p', q_1)_{c'} \in \Phic
%\mathrm{~is~the~partial~application~}
%x_c \mapsto \weic(q_0, p, x_c, c', p', q_1)}\\[2pt]
%
d_\top(q_1, p, q_3) & \opluseq &
  d_\top(q_1, p, q_2) \otimes d_\top(q_2, p, q_3)\ 
\\
\end{array}
\]
%$\weii(q_2, p, q_3)_a \in \Phic$, for $a \in \Deltai$,
%is the partial application
%$x_c \mapsto \weii(q_2, x_c, p, a, q_3)$.
%
%$\weic(q_0, p, p', q_1)_{c'} \in \Phic$, for $c' \in \Deltac$,
%is the partial application
%$x_c \mapsto \weic(q_0, p, x_c, c', p', q_1)$.
%\caption{Update $d_\bot$ with $\<q_1, q_2>$ or $d_\top$ with $\< q_1, p, q_2>$.}
\caption{The update of $d_\bot$ when $\< q_1, q_2> \notin \Q$.}
\label{fig:best-update-top}
\end{figure}
%
%\noindent
%** effectively computable by hypothesis that the label theory is effective**
%\florent{REVOIR}
Thanks to the hypothesis that $\bar\Phi$ is effective, 
it is possible to construct during the iteration a witness word
for Proposition~\ref{th:best-search}, 
\ie a word $t \in \Delta^*$ with a minimal weight $A(t)$ \wrt~$\leq_\oplus$.

>>>>

%\noindent\quad
%\textbf{for all} $q_0, q_3 \in Q$
\Update $d_\bot$ if $\< q_1, q_2>$ was extracted (Figure~\ref{fig:best-update-bottom}), or \\
\Update $d_\top$ if $\< q_1, p, q_2>$ was extracted (Figure~\ref{fig:best-update-top}).$\;$
}
\caption{Best search for \SWVPA}
\label{algo:Dijkstra}
\end{algorithm}

@@

\begin{figure}[ht]
\(
\begin{array}{lcl}
\multicolumn{3}{l}{%
 \mbox{For~every}\  q_0, q_3 \in Q,}\\[1mm] % if $\< q_1, p, q_2> \notin \Q$
%
d_\bot(q_0, q_3) & \opluseq &
  d_\bot(q_0, q_2) \otimes
  \bigoplus_{\Deltai} \weiei(q_2, q_3)\ 
  \mathrm{if~} \< q_0, q_2> \notin \Q \\
%
d_\bot(q_0, q_3) & \opluseq &
  {\bigoplus_{\Deltac}}
  \bigl(
  \weiec(q_0, p, q_1) \otimes
   d_\top(q_1, p, q_2) \otimes
  \bigoplus_{\Deltar} \weir(q_2, p, q_3)\bigr)\ 
  \mathrm{if~} \< q_1, p, q_2> \notin \Q \\
%
d_\bot(q_0, q_3) & \opluseq &
  d_\bot(q_0, q_2) \otimes
  \bigoplus_{\Deltar} \weier(q_2, q_3)\ 
  \mathrm{if~} \< q_0, q_2> \notin \Q \\ 
%
d_\bot(q_0, q_3) & \opluseq &
  d_\bot(q_0, q_2) \otimes d_\bot(q_2, q_3)\  
  \mathrm{if~} \< q_0, q_2>\notin \Q, \< q_2, q_3> \notin \Q \\[-1mm]
\end{array}
\)
\caption{\textbf{update} $d_\bot$ (Algorithm~\ref{algo:Dijkstra}).}
\label{fig:best-update-bottom}
\end{figure}
%

\begin{figure}[ht]
\(
\begin{array}{lcl}
\multicolumn{3}{l}{%
 \mbox{For~every}\  q_0, q_3 \in Q\ \mbox{and}\ p \in P,}\\[1mm] % if $\< q_1, p, q_2> \notin \Q$
d_\top(q_0, p, q_3) & \opluseq &
  d_\top(q_0, p, q_2) \otimes
  \bigoplus_{\Deltai} \weii(q_2, p, q_3)\
  \mathrm{if~} \< q_0, p, q_2> \notin \Q \\
%\multicolumn{3}{l}{\quad
%\mathrm{where~} \weii(q_2, p, q_3)_a \in \Phic
%\mathrm{~is~the~partial~application~}
%x_c \mapsto \weii(q_2, x_c, p, a, q_3)}\\
d_\top(q_0, p, q_3) & \opluseq &
  {\bigoplus^2_{\Deltac}}
  \bigl[ \bigl( \weic(q_0, p, q_1, p) \otimes_2
  d_\top(q_1, p', q_2) \bigr) \otimes_2
  {\bigoplus_{\Deltar}} \weir(q_2, p', q_3) \bigr]\
  \mathrm{if~} \< q_1, p', q_2> \notin \Q \\
%\multicolumn{3}{l}{\quad
%\mathrm{where~} \weic(q_0, p, p', q_1)_{c'} \in \Phic
%\mathrm{~is~the~partial~application~}
%x_c \mapsto \weic(q_0, p, x_c, c', p', q_1)}\\[2pt]
%
d_\top(q_0, p, q_3) & \opluseq &
  d_\top(q_0, p, q_2) \otimes d_\top(q_2, p, q_3)\ 
  \mathrm{if~} \< q_0, p, q_2> \notin \Q, < q_2, p, q_3> \notin \Q \\[-1mm]
\end{array}
\)
%$\weii(q_2, p, q_3)_a \in \Phic$, for $a \in \Deltai$,
%is the partial application
%$x_c \mapsto \weii(q_2, x_c, p, a, q_3)$.
%
%$\weic(q_0, p, p', q_1)_{c'} \in \Phic$, for $c' \in \Deltac$,
%is the partial application
%$x_c \mapsto \weic(q_0, p, x_c, c', p', q_1)$.
%\caption{Update $d_\bot$ with $\<q_1, q_2>$ or $d_\top$ with $\< q_1, p, q_2>$.}
\caption{\textbf{update} $d_\top$ (Algorithm~\ref{algo:Dijkstra}).}
\label{fig:best-update-top}
\end{figure}
%
%\noindent
%** effectively computable by hypothesis that the label theory is effective**
%\florent{REVOIR}
Thanks to the hypothesis that $\bar\Phi$ is effective, 
it is possible to construct during the iteration a witness word
for Proposition~\ref{th:best-search}, 
\ie a word $t \in \Delta^*$ with a minimal weight $A(t)$ \wrt~$\leq_\oplus$.
